Paper Visualizations

### 2022-05-23 eda/paper-graphics.Rmd
graph format pending holly

---
title: "Paper Visualizations"
author: "Amanda Konet"
date: "`r date()`"
output:
  html_document:
    df_print: paged
---

@@

stargazer(forg_privacy, forg_privacy_interactions, forg_undue, forg_undue_interactions, lif_undue, lif_undue_interactions, relauo_undue, relauo_undue_interactions,
          title="Results", type='html',align=TRUE,
          column.labels = c("Model 1", "Model 2", 
                            "Model 3", "Model 4", "Model 5", "Model 6", 
                            "Model 7", "Model 8"))
# , covariate.labels = c("Justice Ideology", "Justice Gender", "Lower Court Decision", "Solicitor General Amicus Brief", "pfemam", "forgauf_privacy", "justicemq:forgauf_privacy", "forgauf_undue_burden", "justicemq:forgauf_undue_burden", "poppam", "lifauo_undue_burden", "justicemq:lifauo_undue_burden"))
```

@@

stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality
          ,title="Results", type='html',align=TRUE,
          column.labels = c("Model 1", "Model 2", 
                            "Model 3", "Model 4", "Model 5"))
```

>>>>

---
title: "Paper Visualizations"
author: "Amanda Konet"
date: "`r date()`"
output:
  html_document
---

@@

stargazer(forg_privacy, forg_privacy_interactions,
          forg_undue, forg_undue_interactions,
          lif_undue, lif_undue_interactions,
          relauo_undue, relauo_undue_interactions,
          type='html',align=TRUE,
          model.numbers = F, ci=T,
          dep.var.labels="Justice Vote (1 = Fem)",
          column.labels = c("Model 1", "Model 2", 
                            "Model 3", "Model 4", "Model 5", "Model 6", 
                            "Model 7", "Model 8"),
          order=c("forgauf_privacy", "justicemq:forgauf_privacy",
                  "forgauf_undue_burden", "justicemq:forgauf_undue_burden",
                  "lifauo_undue_burden", "justicemq:lifauo_undue_burden",
                  "relauo_undue_burden", "justicemq:relauo_undue_burden",
                  "justicemq","justicefem1","pfemam","poppam","sgfem3","lcdisdirfem1"),
          covariate.labels = c("feminist privacy","justice ideology X feminist privacy",
                               "feminist undue burden", "feminist undue burden x justice ideology",
                               "AA org undue burden", "AA org undue burden x justice ideology",
                               "religious (AA) undue burden", "religious (AA) undue burden X justice ideology",
                               "justice ideology", "justice gender", "proportion RR", "proportion AA",
                               "SG amicus brief", "lower court decision"),
          out="graphics/table2.htm")
```

@@

stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality,
          title="Results", type='html',align=TRUE,
          column.labels = c("Model 1", "Model 2", 
                            "Model 3", "Model 4", "Model 5"))
```
